---
title: "Homework 5"
author: "Safiya Sirota"
date:  2021-11-20
output: 
  github_document:
    toc: TRUE
---

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
library(patchwork)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

__Importing and cleaning the data__

```{r}
homicide_df <-
  read_csv("./data/homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved"
    )
    ) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
```

__Focusing on Baltimore, MD__

```{r}
baltimore_df <-
  homicide_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary <-
  baltimore_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )

baltimore_test <-
  prop.test(
    x = baltimore_summary %>% pull(unsolved),
    n = baltimore_summary %>% pull(n)
  )

baltimore_test %>% 
  broom::tidy()

```

Let's try to iterate across cities!

First off, write a function.

```{r}
prop_test_function <- function(city_df) {

  city_summary <-
    city_df %>% 
      summarize(
        unsolved = sum(resolution == "unsolved"),
        n = n()
      )

  city_test <-
    prop.test(
      x = city_summary %>% pull(unsolved),
      n = city_summary %>% pull(n)
    )
  
 return(city_test)
  
}
  
prop_test_function(baltimore_df)

homicide_df %>% 
  filter(city_state == "AlbuquerqueNM") %>% 
  prop_test_function()
```

Now, let's iterate across all cities.

```{r}
results_df <-
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```


Try to make a plot showing estimates and confidence intervals.

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +   
  geom_point() +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

## Problem 2

Start with a dataframe containing all file names; the list.files function will help

Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe

Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary

```{r}
#list of filenames
files_df <-
  tibble(
    file = list.files("./data/zip_data")
  )

#making function
read_file <-
  function(filename) {
    
    subject_df <-
      read_csv(str_c("./data/zip_data/", filename))
    
    return(subject_df)
  }

#reading in data
experiment_df <- 
  files_df %>% 
    mutate(
      subj_data = map(file, read_file)
    )

#tidying data
experiment_df <-
  experiment_df %>% 
  unnest(subj_data) %>% 
  mutate(
    arm = as.factor(
      case_when(
      str_starts(file, "con") ~ "control",
      TRUE ~ "experimental"
      )
    ),
    subject_n = case_when(
      arm == "control" ~ as.numeric((str_sub(file, 5, 6))),
      TRUE ~ as.numeric((str_sub(file, 5, 6))) + 10
    )
  ) %>% 
  select(-file) %>% 
  relocate(subject_n, arm) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "value",
    names_prefix = "week_"
  )
```

__Making spaghetti plot__

```{r}
experiment_df %>% 
  ggplot(aes(x = week, y = value, group = as.factor(subject_n), color = arm)) +
  geom_line()
```


## Problem 3

```{r}
set.seed(10)

iris_with_missing <-
  iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>% 
  mutate(Species = as.character(Species))
  
```

